MSc Statistical Rob correction -Jan29

### 2018-02-09 MSc_Statistical_Rob_correction_-Jan29.Rmd
Models putting everything together!

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)
library(mefa)
library(ggbiplot)
library(pvclust)
library(vegan)
library(ggbiplot)
```

@@

@@

### Root size
```{r}
Root_size <-read.csv("CSV/Root_size.csv")
```

@@

### PCA
```{r}
colnames(FloristicSurvey)[1] <- "Population" # population loads in weirdly, I am just arranging it to not have quotes around. so odd
FloristicSurvey$Population<-as.factor(FloristicSurvey$Population) # Make the population a factor and not an interger
FloristicSurvey[is.na(FloristicSurvey)] <- 0
sum(row.has.na <- apply(FloristicSurvey, 1, function(x){any(is.na(x))}))

# Start the PCA
PC <- prcomp(FloristicSurvey[,4:ncol(FloristicSurvey)], center=T)
summary(PC)
screeplot(PC)

# Variation explaination
100*sum(summary(PC)[[1]][1])/sum(summary(PC)[[1]]) #explained by just PC1
100*sum(summary(PC)[[1]][1:2])/sum(summary(PC)[[1]])#explained by PC1 and PC2
n=25
100*sum(summary(PC)[[1]][1:n])/sum(summary(PC)[[1]])
```

@@

## finally plotting.
mult <- 1 #multiplier for the arrows and text for envfit below. You can change this and then rerun the plot command.
FloristicSurvey.nmds.gg1 <- ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ 
    geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, alpha=df_ell.FSurvey.GM_coverage$GM_coverage))+ 
    scale_alpha_manual(guide = FALSE,values=c(0.3, 0.5, 0.6, 0.7))+ 
    geom_point( aes(shape = FloristicSurvey.NMDS.data$GM_Coverage), size = 1)+ 
    annotate("text",x = NMDS.mean.FloristicSurvey$NMDS1,y = NMDS.mean.FloristicSurvey$NMDS2,label=NMDS.mean.FloristicSurvey$group)+ 
    geom_segment(data = env.scores.FloristicSurvey,aes(x = 0, xend = mult*env.scores.FloristicSurvey$NMDS1, y = 0, yend = mult*env.scores.FloristicSurvey$NMDS2),arrow = arrow(length = unit(0.25, "cm")), colour = "grey")+ 
    geom_text(data = env.scores.FloristicSurvey,aes(x = mult*env.scores.FloristicSurvey$NMDS1, y = mult*env.scores.FloristicSurvey$NMDS2, label=env.variables),size = 5, hjust = -0.5)+ 
    scale_shape_manual(values = c(1,8,19,5))+ 
    coord_cartesian(xlim = c(-1,1.5)) 
```

@@

par(mfrow=c(2,2))
ggplot(Soil_characteristics, aes(Location,Agg_stability,fill=Location))+ geom_boxplot() +
  theme_simple()
ggplot(Soil_characteristics, aes(Location,pH,fill=Location))+ geom_boxplot() +
  theme_simple()
ggplot(Soil_characteristics, aes(Location,C_percent,fill=Location))+ geom_boxplot() +
  theme_simple()
ggplot(Soil_characteristics, aes(Location,N_percent,fill=Location))+ geom_boxplot() +
  theme_simple()

```
# Histology data Analysis

@@

# Combining histology and field data

>>>>

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)
library(mefa)
library(ggbiplot)
library(pvclust)
library(vegan)
library(ggbiplot)
library(factoextra)
```

@@

FloristicSurvey$Population<-as.factor(FloristicSurvey$Population) # Make the population a factor and not an interger
FloristicSurvey[is.na(FloristicSurvey)] <- 0
sum(row.has.na <- apply(FloristicSurvey, 1, function(x){any(is.na(x))}))

@@

### Root size
```{r}
Root_size <-read.csv("CSV/Root_size.csv")
Root_size$pop<-gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",Root_size$indiv)
Root_size$location<-gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",Root_size$indiv)
Root_size$species<-gsub("^[0-9]+[I,O]([A-Z]+).*","\\1",Root_size$indiv)
Root_size$location<-as.factor(Root_size$location)
Root_size$species<-as.factor(Root_size$species)
Root_size$pop<-as.factor(Root_size$pop)
```

@@

@@

## finally plotting.
mult <- 1 #multiplier for the arrows and text for envfit below. You can change this and then rerun the plot command.
ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ 
    geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, color=df_ell.FSurvey.GM_coverage$GM_coverage))+ 
    geom_point( aes(color = FloristicSurvey.NMDS.data$GM_Coverage), size = 1)+ 
    scale_color_manual(values = c(14,5,19,2))+ 
    coord_cartesian(xlim = c(-1,1.5))+
  theme_simple()+ guides(color=guide_legend("Garlic Mustard Coverage"))
```
### PCA
```{r}
FloristicSurvey<-FloristicSurvey[,-56]
FloristicSurvey.pca <- prcomp(FloristicSurvey[,4:(ncol(FloristicSurvey))],center = TRUE) 
summary(FloristicSurvey.pca)
fviz_eig(FloristicSurvey.pca,addlabels=TRUE,hjust = -0.3)+theme_simple()

round(FloristicSurvey.pca$sdev^2/sum(FloristicSurvey.pca$sdev^2)*100,2)
# About 25% explained by my first 2 eigenvectors. 50% by the first 6.
```
### Modeling (redundancy analysis)
species comp ~ GMcov * pop + soil characteristics inside and outside as covariates? 
```{r}

species<-names(FloristicSurvey[4:(length(FloristicSurvey))])
SpeciesGMCorrelation <- data.frame(matrix(ncol = 3, nrow = 0))
names(SpeciesGMCorrelation)<-c("Species", "PValue","signif")

for(i in 4:(length(FloristicSurvey))){
  SpeciesGMCorrelation[i-3,1]<-names(FloristicSurvey[i])
  SpeciesGMCorrelation[i-3,2]<-summary(glm(FloristicSurvey[,i]~GM_Coverage, data=FloristicSurvey, family = binomial))$coefficients[8]
}
for(i in 1:length(species)) if( SpeciesGMCorrelation[i,2] <= 0.05){
  SpeciesGMCorrelation[i,3]<-c("TRUE")
}else{
  SpeciesGMCorrelation[i,3]<-c("FALSE")
  }
length(SpeciesGMCorrelation$signif[SpeciesGMCorrelation[,3]==TRUE])/length(SpeciesGMCorrelation$signif)*100
SpeciesGMCorrelation$Species[SpeciesGMCorrelation[,3]==TRUE]

# Redundancy analysis
sp.comp <- FloristicSurvey[,4:(length(FloristicSurvey))]
var <- FloristicSurvey[,1:3]
var$Quadrat <- as.character(var$Quadrat)
for(i in 1:length(var$Quadrat))if(var$Population[i] == "7"){
  var$Quadrat[i]<-paste("7",var$Quadrat[i],sep="")
}else if(var$Population[i] == "3"){
  var$Quadrat[i]<-paste("3",var$Quadrat[i],sep="")
}else if(var$Population[i] == "14"){
  var$Quadrat[i]<-paste("14",var$Quadrat[i],sep="")
}else if(var$Population[i] == "13"){
  var$Quadrat[i]<-paste("13",var$Quadrat[i],sep="")
}else if(var$Population[i] == "1"){
  var$Quadrat[i]<-paste("1",var$Quadrat[i],sep="")
}

var$Population <- as.factor(var$Population)

formulaRDA <- rda(sp.comp ~ GM_Coverage + Condition(Population) , data=var)

formulaRDA <- rda(sp.comp ~ GM_Coverage , data=var)
head(summary(formulaRDA))
RsquareAdj(formulaRDA)
plot(formulaRDA, scaling = 2)
anova.cca(formulaRDA,step=1000)
anova.cca(formulaRDA,by="axis", step=1000)

```
*Note that I redid this with GM_coverage_catogory and i didnt find ANY significance!

@@

par(mfrow=c(2,2))
ggplot(Soil_characteristics, aes(Location,Agg_stability,fill=Location))+ geom_boxplot() +
  theme_simple()
ggplot(Soil_characteristics, aes(Location,pH,fill=Location))+ geom_boxplot() +
  theme_simple()
ggplot(Soil_characteristics, aes(Location,C_percent,fill=Location))+ geom_boxplot() +
  theme_simple()
ggplot(Soil_characteristics, aes(Location,N_percent,fill=Location))+ geom_boxplot() +
  theme_simple()
Soil_characteristics$Population<-as.factor(Soil_characteristics$Population)

GLMER_soil <- glmer(Location~scale(Agg_stability)*scale(C_percent)*scale(N_percent)+(1|Population),family=binomial(link='logit'),data=Soil_characteristics)
summary(GLMER_soil)
options(na.action = "na.fail")
dredge(GLMER_soil) 
# A model with nothing is best...
```
# Histology data Analysis

@@

## Bring things together

```{r}
Soil_characteristics$Location<-as.character(Soil_characteristics$Location)
for(i in 1:length(Soil_characteristics$Location))if(Soil_characteristics[i,2]=="in"){
   Soil_characteristics[i,2]<-"I"
}else{
  Soil_characteristics[i,2]<-"O"
}
Soil_characteristics$Location<-as.factor(Soil_characteristics$Location)  
names(Soil_characteristics)[1:2]<-c("pop","location")

fulldata <- merge(Soil_characteristics, ndata, by=c("pop","location"))
# note i used the SCALED dataframe for the total histology
fulldata <- merge(fulldata, Root_size, by=c("indiv","location","pop","species"))
for(i in 1:length(fulldata$indiv)){
fulldata$mean_rootsize[i]<-(sum(fulldata[i,20:29])/length(fulldata[,20:29]))
}
fulldata<-fulldata[,-c(20:29)]

binlesionF<-cbind(fulldata$None.Path,100-fulldata$None.Path)
binmycorrF<-cbind(fulldata$None.Myc,100-fulldata$None.Myc)
binherbivoryF<-cbind(fulldata$None.Herb,100-fulldata$None.Herb)

fulldata$pop<-as.factor(fulldata$pop)
# model myc_lesion 
mod1 <- glmmadmb(binlesionF ~ scale(None.Myc)  * scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop), data = fulldata,family = "binomial")
summary(mod1)
mod1.dredge <- dredge(mod1)

# model myc 
mod2 <- glmmadmb(binmycorrF ~ scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop) , data = fulldata,family = "binomial")
summary(mod2)
mod2.dredge <- dredge(mod2)
```
